---
title: "Research of the properties at NewTown in 2017"
author: "500425334"
subtitle: "Project 1"
date: "University of Sydney | DATA1001 | September 2020"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
---

<br>

# Executive Summary

<br>

# Full Report

## Initial Data Analysis (IDA)

Limitation
- 
- 
- 

The Newtown property prices dataset comes from data scraped by [domain](www.domain.com.au) in June 2017. 

```{r}
# Read in the Newtown data
property = read.csv("http://www.maths.usyd.edu.au/u/UG/JM/DATA1001/r/current/data/NewtownJune2017.csv")
str(property)


## Quick snapshot
dim(property)
str(property)
```

<br>

## Research Questions (given)

### What was the average price of a property?

```{r}
# all properties
mean(property$Sold)
```

The average price of a property was 1407.143 dollar

### Does the amount of carspots affect the price?

```{r}
median(property$Sold[property$Carspots=="0"])
median(property$Sold[property$Carspots=="1"])
median(property$Sold[property$Carspots=="2"])

mean(property$Sold[property$Carspots=="0"])
mean(property$Sold[property$Carspots=="1"])
mean(property$Sold[property$Carspots=="2"])
boxplot(property$Sold[property$Carspots=="0"],property$Sold[property$Carspots=="1"],property$Sold[property$Carspots=="2"])
```

Yes, the number of carspotsprop is proportional to the price

###  What were the cheapest properties?

First, we could just sort by the sold price.

```{r}
# Sort all prices
sold = property$Sold
sort(sold)
```

It would nice to list the details about the cheapest properties. Try the following code.

```{r}
attach(property)   # The database is attached to the R search path, so variables in the database can be accessed by simply giving their names.
head(property[order(Sold), ][c(1, 6, 7)], 10)
```
The cheapest properties was 514/88 King Street Newtown with no carspot, which sold 370.
### Assuming commission fees are around 2%, which agency earnt the most over that period? 

```{r}
# Example of extracting Agent sales
sort(tapply(property$Sold, INDEX = property$Agent, sum)*0.02)
```
RayWhite earnt 347.62 dollar, which is the most in the agents.

## Research Question (own)





